\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-03-08 paper/wireframe/wireframe.tex
Background and Significance

\section{Background \& Significance}
This is where you explain the context of your paper and describe in detail why it's important. It can be melded into your introduction or you can create a separate section to help with the organization and narrative flow of your paper. Approach writing this section with the thought that you can’t assume your readers will know as much about the research problem as you do. Note that this section is not an essay going over everything you have learned about the topic; instead, you must choose what is most relevant in explaining the aims of your research.

To that end, while there are no prescribed rules for establishing the significance of your proposed study, you should attempt to address some or all of the following:

>>>>

\section{Background \& Significance}
Our research problem is to take different discovered and undiscovered exploits and test them against Lenel Blue Diamond readers. The purpose of this study is to uncover different vulnerabilities in Lenel Blue Diamond readers so that they can be disclosed properly and eventually patched. Lenel has over 1 million Blue Diamond readers deployed in multiple industries, the most notable one being real-estate (https://www.lenel.com/products/bluediamond). This study is important because the security of these locks are very important because if someone unauthorized is able to enter through these locked doors, everything on the other side would be compromised including important data, objects, and even people. Things which if they were compromised would result in extreme loss. For our research the major issues we found fall into three categories, the firmware used on the lock, the physical aspect of the lock, and the usage of the mobile app and bluetooth communication. We plan to conduct our research by using trusted sources on the subject and testing their conclusions on Lenel Blue Diamond readers. We plan to conduct our research by using trusted sources on the subject and testing their conclusions on Lenel Blue Diamond readers. Our research has it bounds inside the Lenel Blue Diamond readers mobile app and lock itself. We will not be researching the server side of lenel Blue Diamond readers and are assuming that the server side is secure for this research project.
